oREVIRT analysis

### 2022-11-18 analysis/irt_analysis.Rmd
add cor with frequ data

>>>>

# Correlation item difficulty and frequency

```{r}
plot_dif <- coef(irt1_guess)$targetWord %>%
	as_tibble(rownames = "targetWord")%>%
  left_join(
    data%>%select(targetWord, german, aoa_german_comb)%>%distinct(targetWord, german, aoa_german_comb)%>%
      left_join(read_xlsx("../data/childLex_0.17.01c_2018-12-24_schr.xlsx", sheet = 2)%>%rename(german = lemma)%>%mutate(german = tolower(german), german = ifelse(german == "türe", "tür", german))%>%select(-type))%>%
      distinct(targetWord, german, aoa_german_comb, .keep_all = T)%>%
      select(-pos, -bigram.min, -bigram.sum, -nei.old20, -nei.n, -n.syl,-n.letters, -cd, -atype.abs, -type.abs, -lemma.abs)%>%
      pivot_longer(cols = c(aoa_german_comb, atype.norm, type.norm, lemma.norm), names_to = "type", values_to = "value")%>%
      group_by(type)
    )

plot_dif%>%
  #filter(german != "tür", 
   #      german != "auge")%>%
  ggplot(aes(x = value, y = Estimate.eta_Intercept))+
  geom_point(pch = 1)+
  facet_wrap(~type, scales = "free_x")+
  stat_cor()+
  theme_bw()
